A minimal reaction-diffusion neural model generates {\emph{C. elegans}} undulation

### 2020-12-26 paper.tex
add caption for worm neuron dash

\begin{figure}[h!]
    \centering
    \includegraphics[height=13cm]{figures/worm_neuron_dash/worm_neuron_dash.pdf}
    \caption{TODO}
    \label{fig: worm_neuron_dash}
\end{figure}

>>>>

\begin{figure}[h!]
    \centering
    \includegraphics[height=13cm]{figures/worm_neuron_dash/worm_neuron_dash.pdf}
    \caption{A "dashboard view" representing the neuron and worm.  (a) shows the potentials of the ventral neurons, coloured by number running down the worm.  (b) shows "images" of the simulated worm at different timepoints.  The worm was simulated by running the neuron potentials through a Gaussian filter to simulate muscle dampening, then taking the amplitude as an angular displacement, representing contraction or relaxation.  (c) shows images of a real \emph{C. elegans} in a cuvette, taken via shadow imaging.}
    \label{fig: worm_neuron_dash}
\end{figure}
